---
title       : Weight for It - Convert Between Kilos and Pounds using RShiny
author      : V. Felipe
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

--- .class "Slide2"

## Introduction
### This was created using RShiny for Coursera's Developing Data Products project


```{r, echo=FALSE, eval=TRUE}
print(as.character(paste("Date created:", format(Sys.Date(), "%B %d, %Y"))))
```

--- .class "Slide3"

## About the Application
### The UI prompts the user for the weight (slider) with the corresponding unit of measure (dropdown). The main panel will display the converted weight. If the selected unit of measure was kilos then the main panel will show the weight converted to pounds (and vice-versa).

```{r, echo=TRUE, eval=FALSE}
output$outval <- renderText(if (input$unit =="kg") { input$unitval * 2.2046 } 
    else { input$unitval / 2.2046 })
```

--- .class #Slide4

## How to Use
1. In the left panel, choose unit of measure (kg or lb)
2. Choose weight amount to be converted
3. The main panel will show the converted weight

--- .class #Slide5

## Thank You
* Shiny App: https://vfelipe.shinyapps.io/CourseraDDP-RShiny/
* Source: https://github.com/vfelipe/coursera-ddp

